\documentclass{article}

\begin{document}
 \section*{Design aims of C++ with comments}
 \begin{itemize}
  \item \textbf{Close to the Hardware}: fundamental types (eg.: \texttt{bool}, \texttt{int}, \texttt{char} etc.) 
  are in the language to support manipulating hardware resources directly without extra overhead.
  \\
  $\Rightarrow$ if a structure is based on a \texttt{char} (1 byte) and an \texttt{int} (4 bytes), then that will consume
  5 bytes of memory.
  \\
  On top of that, inline functions are supported without causing extra call overhead, as compile time constants supported too.
  \item \textbf{Allows Ideas to be Expressed in Code}: C++'s abstraction mechanisms are for supporting the 
  programmer to express ideas, relationships with abstraction mechanisms such as:
  \begin{itemize}
    \item \textbf{Classes} - Custom (aka. User Defined) types (eg.: Polygon) that support direct representation built from fundamental primitive types.
    \item \textbf{Abstract Classes} - General Concepts that cannot be represented directly (eg.: Shape) that provides inheritance support.
    \item \textbf{Inheritance} - To provide specialized classes from more generalized base classes (eg. Polygon inherits from Shape).
    \item \textbf{Relationships} - To identify relationships between ideas by the usage of Class Hierarchies (eg. inheritence chain).
  \end{itemize}
 \item \textbf{Efficient, Platform Independent and Backward and C Compatible}: very little overhead can be found at certain features (eg.: VTBL [virtual table lookups]),
 and many compiler implementations exist on many different platforms. The new versions are backward compatible,
 and C-compatibilty (as C is subset of C++) is maintained for not breaking any existing (millions of billions) lines of C++ code.
 \item \textbf{Supports Generalized Programming}: by supporting Templates, C++ provides help in building foundation libraries. The STL is a great example for that.
 \item \textbf{Type Safety}: Primitive and User Defined types are being checked at compile time (C++ is a strongly typed language).
 \end{itemize}

\end{document}
