\documentclass{article}

\begin{document}
 \section*{Five language features offered by C++ 1985}
 Ordered by importance with commenting their role in programming.
 \begin{enumerate}
  \item \textbf{Classes and Derived Classes} \- Enables to represent user defined types.
  \item \textbf{Public / Private access control} \- Enables information hiding and user interface.
  \item \textbf{Constructors and Destructors} \- Enables concise resource handling and class invariant.
  \item \textbf{Operator / Function Overloading} \- Simplifies and reduces the amount of code that needs to be written.
  \item \textbf{Virtual Functions} \- Enables to define general types without concrete implementation $\Rightarrow$ abstract classes.
 \end{enumerate}
 
 \section*{Five language features offered by C++98}
 Ordered by importance with commenting their role in programming.
 \begin{enumerate}
  \item \textbf{RAII} \- Resource Acquisition Is Initialization $\Rightarrow$ Copy and Assignment constructors.
  \item \textbf{Exceptions} \- Enables to propagate program errors in an elegant way without requiring the need to handle those errors locally.
  \item \textbf{Templates} \- Enables class and function objects to be created with type arguments. Requires runtime support.
  \item \textbf{Namespaces} \- Enables logical distinction of parts of the program.
  \item \textbf{STL} \- Adds support for handling common tasks with containers and algorithms.
 \end{enumerate}
 
 \section*{Five language features offered by C++11}
 Ordered by importance by commenting on their role in programming.
 \begin{enumerate}
  \item \textbf{Resource Management Pointers} \- Unique and Shared pointers. Moving objects by pointers from one scope to another and having reference counter pointers without a certain owner.
  \item \textbf{Move Semantics} \- Moving objects by reference without copying large objects.
  \item \textbf{Lambda Expressions} \- Anonymous function objects (delegates) to support functions that accept delegates.
  \item \textbf{Concurrency Compliant Memory Model} \- To support writing applications with multiple threads in a multiprocessor environment.
  \item \textbf{Type Deduction with \texttt{auto}} \- To reduce the amount of code that needs to be written. Improves readability.
 \end{enumerate}
\end{document}